SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-13 scipy-1.0/paper.tex
Add linguist citation

Python, Cython, Fortran, C and C++ are the programming languages used to
implement scientific algorithms in the SciPy library. An analysis of our code
base using the \texttt{linguist} library provides a detailed breakdown as \%
composition by programming language in SciPy (Figure~\ref{fig:linguist}).

>>>>

Python, Cython, Fortran, C and C++ are the programming languages used to
implement scientific algorithms in the SciPy library. An analysis of our code
base using the \texttt{linguist} library\cite{linguistref} provides a 
detailed breakdown as \% composition by programming language in 
SciPy (Figure~\ref{fig:linguist}).
